Jackknife

### 2021-02-24 analysis/rev_prototyping/jacknife_results.Rmd
fia results

<!-- ```{r, fig.dim = c(6,6)} -->

>>>>

```{r, fig.dim = c(8,8)}

fia_max_n = 150
fia_max_s = 21

ggplot(jk_di_mean_results, aes(s0, n0, color = dat)) +
  geom_point(aes(s0_actual, n0_actual), color = "grey", alpha  = .2)+
    geom_point(aes(s0, n0, color = dat), alpha = .5) +
  theme_bw() +
  scale_x_log10() +
  scale_y_log10() +
  facet_wrap(vars(dat)) +
  geom_vline(xintercept = fia_max_s) +
  geom_hline(yintercept = fia_max_n) +
  theme(legend.position = "top")

jk_di_mean_results <- jk_di_mean_results %>%
  group_by_all() %>%
  mutate(fiasized = (s0 <= fia_max_s) && (n0 <= fia_max_n),
         fiasized_acutal =(s0_actual <= fia_max_s) && (n0_actual <= fia_max_n) ) %>%
  ungroup()

jk_di_mean_results %>%
  group_by(dat) %>%
  summarize(jk_small = mean(fiasized), actual_small = mean(fiasized_acutal), nsites = dplyr::n())

jk_di_mean_results %>%
  group_by(dat, fiasized) %>%
  summarize( nsingletons_high  = mean(nsingletons_percentile_excl > 95), nsites = dplyr::n())

```
<!-- ```{r, fig.dim = c(6,6)} -->
